---
title: "Stat. vs. Semi-mech. vs. Mechanistic (Compartmental)"
output: html_document
date: '2022-07-24'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, echo = FALSE}
library(here)
library(masterthesis)
library(scoringutils)
library(ggplot2)
library(RColorBrewer)
library(lme4)
library(lmerTest)
library(dplyr)
source(here("code", "load_clean_data.R"))

case_data <- hub_data |>
  filter(target_type == "Cases", 
         availability > 0.15)

death_data <- hub_data |>
  filter(target_type == "Deaths",
         availability > 0.15)
```



## Cases
### Distribution of difference in relative scores
```{r, include = FALSE}
case_scores <- case_data |>
  filter(!model_type == "ensemble") |>
  score() |>
  summarise_scores(by = c("model_type", "forecast_date", "horizon")) |>
  select(model_type, forecast_date, horizon, interval_score) |>
  #group_by(model_type, forecast_date, horizon,quantile) |>
  #summarise(interval_score = mean(interval_score)) |>
  ungroup() |>
  arrange(model_type, forecast_date)


bl_rel <- case_scores |> 
  filter(model_type == "baseline") |>
  rename(bl_score = interval_score) |>
  select(-model_type)

rel_case_scores <- case_scores |>
  filter(!model_type == "baseline") |>
  left_join(bl_rel, by = c("forecast_date", "horizon")) |>
  mutate(rel_score = interval_score / bl_score)
```

```{r, echo = FALSE}
ggplot(rel_case_scores, aes(x = rel_score, color = model_type)) +
  geom_density() +
  facet_wrap(~horizon) +
  scale_color_brewer(palette = "Set1") +
  xlim(0,6)
  
```


### Pairwise comparisons
```{r pw_c1, fig.height = 8, fig.width = 5, echo = FALSE}
all_scores <- case_data |>
 score() |>
 summarise_scores(by = c("model_type", "forecast_date", "quantile", "location", "target_type", "horizon")) 
pw_comp <- all_scores |>  
   filter(!model_type == "ensemble") |>
   rename(model = model_type) |>
   pairwise_comparison(by = c("model", "horizon", "target_type"),
                       baseline = "baseline") |>
   plot_pairwise_comparison() +
   facet_wrap(~horizon + target_type, ncol = 2)
pw_comp
```


### Pairwise comparison with other split

```{r pw_c2, fig.height = 8, fig.width = 5, echo = FALSE}
all_scores <- hub_data |>
  mutate(model_type = ifelse(model %in% c("MOCOS-agent1", "ICM-agentModel"),
                             "agent-based", model_type)) |>
 score() |>
 summarise_scores(by = c("model_type", "forecast_date", "quantile", "location", "target_type", "horizon")) 
pw_comp <- all_scores |>  
   filter(!model_type == "ensemble") |>
   rename(model = model_type) |>
   pairwise_comparison(by = c("model", "horizon", "target_type"),
                       baseline = "baseline") |>
   plot_pairwise_comparison() +
   facet_wrap(~horizon + target_type, ncol = 2)
pw_comp
```


### Model Types vs. Baseline

```{r, echo = FALSE}
scores_hub <- case_data |>
  score() |>
  summarise_scores(by = c("model_type", "location", "target_type","horizon", "forecast_date")) |>
  filter(!model_type %in% c("other", "ensemble")) |>
  mutate(model_type = relevel(as.factor(model_type), ref = "baseline"))
```


```{r baseline_pred, echo = FALSE}
mt_against_bl <- lmer(interval_score ~ model_type + horizon  + (1|forecast_date) + (1|location),
     data = scores_hub)
summary(mt_against_bl)
```
- Include RE for forecast_date to remove individual idiosyncracies
- 

### Remove baseline, use statistical model type as reference
```{r stat_as_ref, echo = FALSE}
scores_hub_wobl <- scores_hub |>
  filter(!model_type %in% c("baseline", "ensemble")) |>
  mutate(model_type = relevel(as.factor(model_type), ref = "statistical"))


mt_against_stat <- lmer(interval_score ~ model_type + horizon  + (1|forecast_date) + (1|location),
              data = scores_hub_wobl)
summary(mt_against_stat)
```
### Interaction model type and horizon
```{r baseline_pred_by_hor, echo = FALSE}
scores_hub <- scores_hub |>
  mutate(long_hor = ifelse(horizon %in% c(3,4), 1, 0))

mt_against_bl <- lmer(interval_score ~ model_type + long_hor +  model_type:long_hor + (1|forecast_date) + (1|location),
     data = scores_hub)
summary(mt_against_bl)
```


# Plot scores of semi mechanistic models
```{r calc_semi_scores, include = FALSE}
case_scores_semi <- case_data |>
  filter(model_type %in% c("baseline", "semi")) |>
  score() |>
  summarise_scores(by = c("model", "forecast_date", "horizon")) |>
  select(model, forecast_date, horizon, interval_score) |>
  arrange(model, forecast_date)


bl_rel <- case_scores_semi |> 
  filter(model == "EuroCOVIDhub-baseline") |>
  rename(bl_score = interval_score) |>
  select(-model)

rel_case_scores_semi <- case_scores_semi |>
  filter(!model == "EuroCOVIDhub-baseline") |>
  left_join(bl_rel, by = c("forecast_date", "horizon")) |>
  mutate(rel_score = interval_score / bl_score) |>
  mutate(horizon_group = factor(ifelse(horizon %in% c(1,2),
                                 "short", "long"),
                                levels = c("short", "long")))
```

```{r semi_scores, echo = FALSE}
ggplot(rel_case_scores_semi, aes(x = rel_score, color = model)) +
  geom_density() +
  facet_wrap(~horizon_group) +
  scale_color_brewer(palette = "Set1") +
  xlim(0,4)
```


### Regression of WIS decomposition components
```{r , echo = FALSE}
scores_hub_wobl <- scores_hub |>
  filter(!model_type %in% c("baseline", "ensemble")) |>
  mutate(model_type = relevel(as.factor(model_type), ref = "statistical"))


mt_against_stat <- lmer(underprediction ~ model_type + horizon  + (1|forecast_date) + (1|location),
              data = scores_hub_wobl)
summary(mt_against_stat)
```

```{r, echo = FALSE}
scores_hub_wobl <- scores_hub |>
  filter(!model_type %in% c("baseline", "ensemble")) |>
  mutate(model_type = relevel(as.factor(model_type), ref = "statistical"))


mt_against_stat <- lmer(overprediction ~ model_type + horizon  + (1|forecast_date) + (1|location),
              data = scores_hub_wobl)
summary(mt_against_stat)
```
```{r tst1, echo = FALSE}
scores_hub_wobl <- scores_hub |>
  filter(!model_type %in% c("baseline", "ensemble")) |>
  mutate(model_type = relevel(as.factor(model_type), ref = "statistical"))


mt_against_stat <- lmer(dispersion ~ model_type + horizon  + (1|forecast_date) + (1|location),
              data = scores_hub_wobl)
summary(mt_against_stat)
```
### Plot decomposition of WIS for model types
```{r wis decomp, echo = FALSE }
case_scores <- hub_data |>
  filter(!model_type %in% c("other", "ensemble")) |>
  score() |>
  summarise_scores(by = c("model_type", "horizon", "target_type")) |>
  select(model_type, horizon, target_type, interval_score, overprediction, underprediction, dispersion) |>
  ungroup() |>
  arrange(model_type) 

bl_rel <- case_scores |> 
  filter(model_type == "baseline") |>
  rename(bl_score = interval_score) |>
  select(horizon, target_type, bl_score) 

rel_scores<- case_scores |>
  filter(!model_type == "baseline") |>
  left_join(bl_rel, by = c("horizon", "target_type")) |>
  mutate(rel_op = overprediction / bl_score,
         rel_up = underprediction / bl_score,
         rel_disp = dispersion / bl_score) |>
  select(model_type, horizon, target_type, rel_op, rel_up, rel_disp) |>
  melt(id.vars = c("model_type", "horizon", "target_type"))

ggplot(rel_scores, aes(x = model_type, y = value, fill = variable)) +
  geom_bar(position="stack", stat="identity") +
  facet_wrap(~horizon+target_type, ncol = 4) +
  geom_hline(yintercept = 1) +
  scale_x_discrete(name = "Model Type",
                   breaks=c("mechanistic","semi","statistical"),
        labels=c("mech.", "semi", "stat.")) +
  scale_y_continuous(name = "WIS, relative to baseline model") +
  scale_fill_brewer(palette = "Set2",
                    labels = c("Overpred.",
                               "Underpred.",
                               "Disp.")) +
  labs(fill = "WIS components")
```

